\chapter*{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\addcontentsline{toc}{chapter}{CПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begin{enumerate}
    \item \label{itm:harris} Harris, C. A Combined Corner and Edge Detector // Chris Harris, Mike Stephens // Alvey Vision Conference. -- 1988. -- pp. 15-65.
    
    \item \label{itm:lowe} Lowe, D. Distinctive Image Features from Scale-Invariant Keypoints / D. Lowe // International Journal of Computer Vision -- 2004. -- no. 60 (2). -- pp. 91-101.

    \item \label{itm:surf} Bay H., SURF: Speeded up robust features / Bay H., Ess A., Tuytelaars T., Van Gool L. // Computer Vision and Image Understanding -- 2008. -- no. 110. -- pp. 346–359.

    \item \label{itm:brief} Calonder M., BRIEF: Binary Robust Independent Elementary Features / Lepetit V., Strecha C., Fua P. // Proc. European Conference on Computer Vision -- 2010. -- pp. 778–792.

    \item \label{itm:gloh} Kalal Z., Forward-backward error: automatic detection of tracking failures / Kalal Z., Matas J., Mikolajczyk K. // ICPR’10 -- 2010. –- pp. 2756-2759.

    \item \label{itm:orb} Rublee E., ORB: an efficient alternative to SIFT or SURF / Rublee E., Rabaud V., Konolige K., Bradski G. // IEEE International Conference on Computer Vision (ICCV) [Electronic resource] -- 2011. -- Mode of access: \url{http://www.vision.cs.chubu.ac.jp/CV-R/pdf/Rublee_iccv2011.pdf}. -- Date of access: 17.12.2016.

    \item \label{itm:cheeseman} Smith R.C., On the Representation and Estimation of Spatial Uncertainty / Smith R.C., Cheeseman P. // The International Journal of Robotics Research -- 1986. -- no. 5 (4). -- pp. 56–68.
    
    \item \label{itm:ptam} Klein, G. Parallel Tracking and Mapping for Small AR Workspaces / Georg Klein, David Murray. // Proc. International Symposium on Mixed and Augmented Reality (ISMAR) [Electronic resource] -- 2007. -- Mode of access: \url{http://www.robots.ox.ac.uk/~gk/publications/KleinMurray2007ISMAR.pdf}. -- Date of access: 17.06.2017.
    
    \item \label{itm:lsd} Engel, J. LSD-SLAM: Large-Scale Direct Monocular SLAM / J. Engel, T. Schöps, D. Cremers. // European Conference on Computer Vision (ECCV) [Electronic resource] -- 2014. -- Mode of access: \url{https://vision.in.tum.de/_media/spezial/bib/engel14eccv.pdf}. -- Date of access: 15.10.2017.
    
    \item \label{itm:orbslam} Mur-Artal, R. ORB-SLAM: A Versatile and Accurate Monocular SLAM System. / Raúl Mur-Artal, J. M. M. Montiel, Juan D. Tardós // IEEE Transactions on Robotics -- 2015. -- vol. 31, no. 5 -- pp. 1147-1163.
    
    \item \label{itm:svo} Forster, C. SVO: Fast Semi-Direct Monocular Visual Odometry / Christian Forster, Matia Pizzoli, Davide Scaramuzza. // IEEE International Conference on Robotics and Automation (ICRA) [Electronic resource] -- 2014. -- Mode of access: \url{http://rpg.ifi.uzh.ch/docs/ICRA14_Forster.pdf}. -- Date of access: 27.09.2017.
    
    \newpage
    
    \item \label{itm:theia} Sweeney, C. TheiaSfm Source Code and Documentation // Github [Electronic resource] -- 2018. -- Mode of access: \url{http://www.theia-sfm.org/}. -- Date of access: 17.04.2018.

    \item \label{itm:qt} The Qt Company, Qt Documentation // The Qt Company Website  [Electronic resource] -- 2018. -- Mode of access: \url{https://www.qt.io/}. -- Date of access: 20.04.2018.
    
    \item \label{itm:sift} Mordvintsev A., Introduction to SIFT (Scale-Invariant Feature Transform) / A. Mordvintsev, K. Abid // OpenCV Python Documentation [Electronic resource] -- 2013. -- Mode of access: \url{https://goo.gl/5DqpcN}. -- Date of access: 10.11.2017.
OpenCV Сommunity.

    \item \label{itm:opencv} OpenCV Сommunity, OpenCV Source Code // GitHub [Electronic resource] / OpenCV Сommunity -- 2018. -- Mode of access: \url{https://github.com/opencv/opencv}. -- Date of access: 26.09.2017.

    \item \label{itm:last}\label{itm:ros} Open Source Robotics Foundation, Inc., Robot Operation System Documentation [Electronic resource] -- 2018. -- Mode of access: \url{http://wiki.ros.org/}. -- Date of access: 03.05.2018.
\end{enumerate}

\newpage
